\documentclass[10pt]{article}
\usepackage[a4paper, total={7in, 9in}]{geometry}
\usepackage{hanging}
\usepackage{enumitem}
\usepackage{fontspec}
\usepackage{color}
\usepackage{fontawesome}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{academicons}
\usepackage[yyyymmdd]{datetime}

% Environment to place line at bottom of page.
\newenvironment{bottompar}{\par\vspace*{\fill}}{\clearpage}

% Set margins.
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\voffset=-0.125in
\headheight=0.0in
\topmargin=0.0in
\textheight=9.0in

\setmainfont{TeX Gyre Termes}

\renewcommand{\labelitemi}{-}
\renewcommand{\linespread}{1}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

% Set parameters and content.
\definecolor{light-gray}{gray}{0.6}
\newcommand{\namestyle}{\Huge \fontfamily{lmr}\selectfont}
\newcommand{\iconstyle}{\LARGE}
\newcommand{\headstyle}{\scshape \normalsize \textcolor{light-gray}}
\newcommand{\sectionstyle}{\LARGE \fontfamily{lmr}\selectfont}
\newcommand{\at}{\makeatletter @\makeatother}
\newcommand{\textlink}[3][blue]{\href{#2}{\color{#1}{#3}}}

\date{}

\begin{document}

\begin{center}
	\namestyle{TAYLOR SALO}

	\bigskip

	\iconstyle{\href{https://github.com/tsalo}{\faGithubSquare}}
	\enspace
	\iconstyle{\href{https://www.researchgate.net/profile/Taylor_Salo}{\aiicon{researchgate-square}}}
	\enspace
	\iconstyle{\href{https://scholar.google.com/citations?user=YbH1akIAAAAJ}{\aiicon{googlescholar-square}}}
	\enspace
	\iconstyle{\href{https://osf.io/iwpvm/}{\aiicon{osf-square}}}
\end{center}

\begin{minipage}[t]{.5\linewidth}
\flushleft
\headstyle{\href{mailto:tsalo006@fiu.edu}{\nolinkurl{tsalo006@fiu.edu}}}
\end{minipage}
\hfill
\begin{minipage}[t]{.5\linewidth}
\flushright
\headstyle{11200 SW 8th Street, AHC4 380}
\end{minipage}

\begin{minipage}[t]{.3\linewidth}
\flushleft
\headstyle{\href{https://tsalo.github.io}{tsalo.github.io}}
\end{minipage}
\hfill
\begin{minipage}[t]{.7\linewidth}
\flushright
\headstyle{Miami, FL 33199}
\end{minipage}

\bigskip

\begin{center}\sectionstyle{PROFILE}\end{center}

Methodologically oriented cognitive neuroscientist interested in
neuroinformatics. Strong technical skills in neuroimaging data
processing, analysis, and meta-analysis. Passionate about transparency
and reproducibility.

\bigskip

\begin{center}\sectionstyle{EDUCATION}\end{center}

\begin{minipage}[t]{.7\linewidth}
\flushleft
\noindent
\href{https://fiu.edu}{\textbf{Florida International University}},
Doctor of Philosophy,
\href{https://psychology.fiu.edu}{Psychology}
\end{minipage}
\hfill
\begin{minipage}[t]{.3\linewidth}
\flushright
\noindent
\textsc{\textbf{2015 -- present}}
\end{minipage}

\begin{itemize}[noitemsep, nolistsep]
\item
  \href{http://cn.fiu.edu}{Cognitive neuroscience program}
\item
  Advisor:
	\href{https://nbclab.github.io/team/angela-laird}{Dr. Angela Laird}
\end{itemize}

\bigskip

\begin{minipage}[t]{.7\linewidth}
\flushleft
\noindent
\href{https://cornell.edu}{\textbf{Cornell University}},
Bachelor of Arts,
\href{https://www.psych.cornell.edu}{Psychology}
\end{minipage}
\hfill
\begin{minipage}[t]{.3\linewidth}
\flushright
\noindent
\textsc{\textbf{2009 -- 2013}}
\end{minipage}

\begin{itemize}[noitemsep, nolistsep]
\item
  Concentration in behavioral and evolutionary neuroscience
\item
  Advisor:
	\href{http://www.psych.cornell.edu/people/faculty/devoogd-profile/}
	{Dr. Timothy DeVoogd}
\end{itemize}

\bigskip

\begin{center}\sectionstyle{EXPERIENCE}\end{center}

\begin{minipage}[t]{.8\linewidth}
\flushleft
\noindent
\textbf{Graduate Assistant},
\href{https://nbclab.github.io}
{\emph{\textbf{Neuroinformatics and Brain Connectivity Laboratory}}}
\end{minipage}
\hfill
\begin{minipage}[t]{.2\linewidth}
\flushright
\noindent
\textsc{\textbf{2015 -- present}}
\end{minipage}

\href{https://nbclab.github.io/team/laird-angela}{\emph{Dr. Angela Laird}},
\href{http://www.fiu.edu}{\emph{Florida International University}}

\begin{itemize}[noitemsep, nolistsep]
\item
  Currently assisting in the development of a tool for annotation of the
  neuroimaging literature using natural language processing and machine
  learning.
\item
  Currently engaged in a project quantitatively comparing the Neurosynth
  and BrainMap frameworks.
\item
  Providing assistance in the development and implementation of
  neuroimaging data analysis pipelines for several projects within the
  lab.
\end{itemize}

\bigskip

\begin{minipage}[t]{.85\linewidth}
\flushleft
\noindent
\textbf{Junior Specialist},
\href{http://carterlab.ucdavis.edu/front/index.php}
{\emph{\textbf{Translational Cognitive and Affective Neuroscience Laboratory}}}
\end{minipage}
\hfill
\begin{minipage}[t]{.15\linewidth}
\flushright
\noindent
\textsc{\textbf{2013 -- 2015}}
\end{minipage}

\href{http://carterlab.ucdavis.edu/people/carter.php}{\emph{Dr. Cameron Carter}},
\href{https://www.ucdavis.edu}{\emph{University of California, Davis}}

\begin{itemize}[noitemsep, nolistsep]
\item
  Acquired neuroimaging and behavioral data from healthy controls and
  patients with psychosis for projects studying the effects of psychosis
  on cognitive control, emotion regulation, and brain structure.
\item
  Contributed to and maintained a custom codebase for the analysis of
  neuroimaging and behavioral data.
\item
  Processed and analyzed neuroimaging and behavioral data for several
  lab projects.
\item
  Administered behavioral tests and cognitive tasks, including the WASI
  and WRAT, to both control and clinical populations.
\item
  Trained incoming personnel to administer behavioral and cognitive
  tasks.
\end{itemize}

\bigskip

\begin{minipage}[t]{.85\linewidth}
\flushleft
\noindent
\textbf{Lab Co-Manager/Research Assistant},
\emph{\textbf{Laboratory for Lifespan Affective Neuroscience}}
\end{minipage}
\hfill
\begin{minipage}[t]{.15\linewidth}
\flushright
\noindent
\textsc{\textbf{2011 -- 2013}}
\end{minipage}

\emph{Dr. Barbara Ganzel},
\href{http://www.cornell.edu}{\emph{Cornell University}}

\begin{itemize}[noitemsep, nolistsep]
\item
  Contributed to projects investigating functional and structural
  changes associated with subclinical trauma.
\item
  Trained undergraduate students to preprocess and perform data
  diagnostics on fMRI data.
\end{itemize}

\bigskip

\begin{minipage}[t]{.85\linewidth}
\flushleft
\noindent
\textbf{Undergraduate Research Assistant},
\href{http://people.psych.cornell.edu/~devoogdlab/}{\emph{\textbf{Bird Song Behavior Laboratory}}}
\end{minipage}
\hfill
\begin{minipage}[t]{.15\linewidth}
\flushright
\noindent
\textsc{\textbf{2012 -- 2013}}
\end{minipage}

\href{http://www.psych.cornell.edu/people/faculty/devoogd-profile/}{\emph{Dr. Timothy DeVoogd}},
\href{http://www.cornell.edu}{\emph{Cornell University}}

\begin{itemize}[noitemsep, nolistsep]
\item
  Prepared solutions for, and assisted in, intracranial perfusion,
  dissection, and staining of bird brains.
\item
  Examined avian song-related neural regions microscopically.
\end{itemize}

\newpage

\begin{center}\sectionstyle{PUBLICATIONS}\end{center}

\begin{hangparas}{.25in}{1}

	 Yarkoni, T., Markiewicz, C. J., de la Vega, A., Gorgolewski, K. J.,
	 \textbf{Salo, T.}, Halchenko, Y. O., McNamara, Q., DeStasio, K.,
	 Poline, J. B., Petrov, D., Hayot-Sasson, V., Nielson, D. M., Carlin, J.,
	 Kiar, G., Whitaker, K., DuPre, E., Wagner, A., Tirrell, L. S., Jas, M.,
	 Hanke, M., Poldrack, R. A., Esteban, O., Appelhoff, S., Holdgraf, C.,
	 Staden, I., Thirion, B., Kleinschmidt, D. F., Lee, J. A.,
	 Visconti di Oleggio Castello, M., Notter, M. P., \& Blair, R. (2019).
	 \emph{Journal of Open Source Software}, \emph{4}(40), 1294.
	 doi:\textlink{https://doi.org/10.21105/joss.01294}{10.21105/joss.01294}

	\bigskip

	Riedel, M. C., \textbf{Salo, T.}, Hays, J., Turner, M. D., Sutherland, M. T.,
	Turner, J. A., \& Laird, A. R. (2019).
	Automated, efficient, and accelerated knowledge modeling of the cognitive
	neuroimaging literature using the ATHENA toolkit.
	\emph{Frontiers in Neuroscience}, 13, 494.
	doi:\textlink{https://www.frontiersin.org/articles/10.3389/fnins.2019.00494/}{10.3389/fnins.2019.00494}

	\bigskip

	Bartley, J. E., Boeving, E. R., Riedel, M. C., Bottenhorn, K. L.,
	\textbf{Salo, T.}, Eickhoff, S. B., Brewe, E., Sutherland, M. T.,
	\& Laird, A. R. (2018).
	Meta-analytic evidence for a core problem solving network across multiple
	representational domains. \emph{Neuroscience and Biobehavioral Reviews}, 92, 318-337.
	doi:\textlink{https://doi.org/10.1016/j.neubiorev.2018.06.009}{10.1016/j.neubiorev.2018.06.009}

	\bigskip

	Brewe, E., Bartley, J. E., Riedel, M. C., Sawtelle, V., \textbf{Salo, T.},
	Boeving, E. R., Bravo, E. I., Odean, R., Nazareth, A., Bottenhorn, K. L.,
	Laird, R. W., Sutherland, M. T., Pruden, S. M., \& Laird, A. R. (2018).
	Toward a Neurobiological Basis for Understanding Learning in University Modeling
	Instruction Physics Courses. \emph{Frontiers in ICT}, 5, 10.
	doi:\textlink{https://doi.org/10.3389/fict.2018.00010}{10.3389/fict.2018.00010}

	\bigskip

	Ray, K. L., Lesh, T. A., Howell, A. M., \textbf{Salo, T.}, Ragland, J. D.,
	MacDonald, A. W., Gold, J. M., Silverstein, S. M., Barch, D. M., \& Carter,
	C. S. (2017). Functional network changes and cognitive control in schizophrenia.
	\emph{NeuroImage: Clinical}, 15, 161-170.
	doi:\textlink{https://doi.org/10.1016/j.nicl.2017.05.001}{10.1016/j.nicl.2017.05.001}

	\bigskip

	Lopez-Garcia, P., Lesh, T. A., \textbf{Salo, T.}, Barch, D. M., MacDonald,
	A. W., Gold, J., Ragland, J. D., Strauss, M., Silverstein, S., \& Carter, C. S.
	(2016). The neural circuitry supporting goal maintenance during cognitive
	control: a comparison of AX-CPT and dot probe expectancy paradigms.
	\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{16}(1), 164.
	doi:\textlink{https://doi.org/10.3758/s13415-015-0384-1}{10.3758/s13415-015-0384-1}

	\bigskip

	Phillips, R. C., \textbf{Salo, T.}, \& Carter, C. S. (2015). Distinct neural
	correlates for attention lapses in patients with schizophrenia and healthy
	participants. \emph{Frontiers in human neuroscience}, 9.
	doi:\textlink{https://doi.org/10.3389/fnhum.2015.00502}{10.3389/fnhum.2015.00502}

\end{hangparas}

\bigskip

\begin{center}\sectionstyle{PREPRINTS}\end{center}

\begin{hangparas}{.25in}{1}

	Bartley J. E., Riedel M. C., \textbf{Salo T.}, Bottenhorn K. L.,
	Boeving E. R., Laird R. W., Sutherland M. T., Pruden S. M., Brewe E., \&
	Laird A. R. (2019).
	Sex and pedagogy influences in learning-related reorganization of brain activity.
	\emph{bioRxiv}. doi:\textlink{https://doi.org/10.1101/791301}{10.1101/791301}

	\bigskip

	Esteban, O., Ciric, R., Finc, K., Blair, R., Markiewicz, C. J.,
	Moodie, C. A., Kent, J. D., Goncalves, M., DuPre, E., Gomez, D. E. P.,
	Ye, Z., \textbf{Salo, T.}, Valabregue, R., Amlien, I. K., Liem, F.,
	Jacoby, N., Stojić, H., Cieslak, M., Urchs, S., Halchenko, Y. O.,
	Ghosh, S. S., De La Vega, A., Yarkoni, T., Wright, J., Thompson, W. H.,
	Poldrack, R. A., \& Gorgolewski, K. J. (2019).
	Analysis of task-based functional MRI data preprocessed with fMRIPrep.
	\emph{bioRxiv}.
 	doi:\textlink{https://doi.org/10.1101/694364}{10.1101/694364}

	\bigskip

	Gonzalez, A. A., Bottenhorn, K. L., Bartley, J. E., Hayes T., Riedel, M. C.,
	\textbf{Salo, T.}, Bravo, E. I., Odean, R., Nazareth, A., Laird, R. W.,
	Sutherland, M. T., Brewe, E., Pruden, S. M., \& Laird, A. R. (2019).
	Sex differences in brain correlates of STEM anxiety. \emph{bioRxiv}.
	doi:\textlink{https://doi.org/10.1101/528075}{10.1101/528075}

	\bigskip

	Bartley, J. E., Riedel, M. C., \textbf{Salo, T.}, Boeving, E. R.,
	Bottenhorn, K. L., Bravo, E. I., Odean, R., Nazareth, A., Laird, R. W.,
	Sutherland, M. T., Pruden, S. M., Brewe, E., \& Laird, A. R. (2019).
	Brain activity links performance in science reasoning with conceptual
	approach. \emph{bioRxiv}.
	doi:\textlink{https://doi.org/10.1101/526574}{10.1101/526574}

	\bigskip

	Bolt, T., Nomi, J. S., Arens, R., Vij, S. G., Riedel, M. C.,
	\textbf{Salo, T.}, Laird, A. R., Eickhoff, S. B., \& Uddin, L. Q. (2019).
	Ontological Dimensions of Cognitive-Neural Mappings. \emph{bioRxiv}.
	doi:\textlink{https://doi.org/10.1101/524520}{10.1101/524520}

\end{hangparas}

\bigskip

\begin{center}\sectionstyle{PRESENTATIONS}\end{center}

	\begin{hangparas}{.25in}{1}
	\textbf{Salo, T.} (2018).
	NiMARE: A Neuroimaging Meta-Analysis Research Environment.
	Presented at Brainhack Global 2018; Miami, Florida. More
	information \textlink{https://www.slideshare.net/TaylorSalo/nimarebrainhackglobalmiami}{here}.

	\bigskip

	\textbf{Salo, T.}, Riedel, M. C., Bartley, J. E., Bottenhorn, K. L., Yarkoni, T.,
	Turner, M. D., Turner, J. A., Sutherland, M. T., \& Laird, A. R. (2017).
	A quantitative evaluation of Neurosynth's annotation methods. Presented at
	the 23\textsuperscript{rd} annual meeting of the Organization for Human Brain
	Mapping; Vancouver, British Columbia. More information
	\textlink{https://nbclab.github.io/presentations/salo-neurosynth-presentation}{here}.

	\bigskip

	\textbf{Salo, T.}, Riedel, M. C., Bartley, J. E., Bottenhorn, K. L., Yarkoni, T.,
	Turner, M. D., Turner, J. A., Sutherland, M. T., \& Laird, A. R. (2017).
	A quantitative evaluation of Neurosynth's annotation methods. Presented at
	Florida International University's 2017 Graduate Student Scholarly Forum;
	Miami, Florida.

	\bigskip

	\textbf{Salo, T.} \& Renfro, A. (2017). Open science tools: GitHub, BIDS, \&
	preregistration. Presented at Brainhack Global 2017; Miami, Florida. More
	information \textlink{https://osf.io/557vf}{here}.

\end{hangparas}

\bigskip

\begin{center}\sectionstyle{POSTERS}\end{center}

\begin{hangparas}{.25in}{1}

	\textbf{Salo, T.}, Yarkoni T., Kent J. D., Gorgolewski K. J., Glerean E.,
	Bottenhorn K. L., Bilgel M., Wright J., Reeders P., Nielson D. N.,
	Nichols T. E., Riedel M. C., Sutherland M. T., \& Laird A. R. (2019).
	NiMARE: A Neuroimaging Meta-Analysis Research Environment.
	Presented at the 25\textsuperscript{th} annual meeting of the Organization
	for Human Brain Mapping (Rome, Italy).
	More information
	\textlink{https://ww5.aievolution.com/hbm1901/index.cfm?do=abs.viewAbs&abs=4138}{here}.

	\bigskip

	Poudel R., Riedel M. C., \textbf{Salo, T.}, Flannery J. S., Hill L. D.,
	Laird A. R., \& Sutherland M. T. (2019).
	Common and distinct brain regions associated with risky- and ambiguous decision-making.
	Presented at the SANS annual meeting (Miami, Florida).
	More information
	\textlink{https://nbclab.github.io/posters/poudel-sans-poster}{here}.

	\bigskip

	\textbf{Salo, T.}, Bottenhorn K. L., Nichols T. E., Riedel M. C.,
	Sutherland M. T., Yarkoni T., \& Laird A. R. (2018).
	NiMARE: A Neuroimaging Meta-Analysis Research Environment.
	Presented at INCF Neuroinformatics 2018 (Montreal, Quebec) and at the annual
	Brain Initiative Principal Investigators Meeting (Washington D.C.).
	More information
	\textlink{https://f1000research.com/posters/7-1221}{here}.

	\bigskip

	Bottenhorn K. L., \textbf{Salo, T.}, Sutherland M. T., \& Laird A. R. (2018).
	Quantitative comparison of functional decoding approaches across meta-analytic
	frameworks.
	Presented at INCF Neuroinformatics 2018 (Montreal, Quebec).
	More information
	\textlink{https://f1000research.com/posters/7-1222}{here}.

	\bigskip

	Riedel M. C., \textbf{Salo, T.}, Hays J., Turner M. D., Sutherland M. T.,
	Turner J. A., \& Laird A. R. (2018).
	Automating annotations of the cognitive neuroimaging literature using ATHENA.
	Presented at INCF Neuroinformatics 2018 (Montreal, Quebec).
	More information
	\textlink{https://f1000research.com/posters/7-1229}{here}.

	\bigskip

	Yarkoni, T., de la Vega, A., DuPre, E., Esteban, O., Halchenko, Y. O.,
	Hanke, M., Hayor-Sasson, V., Ivanov, A., Kiar, G., Markiewicz, C., McNamara, Q.,
	Petrov, D., \textbf{Salo, T.}, Nielson, D., Poline, J. B., Poldrack, R.,
	\& Gorgolewski, K. (2018).
	Pybids: Python tools for manipulation and analysis of BIDS datasets.
	Presented at the 24\textsuperscript{th} annual meeting of the Organization
	for Human Brain Mapping (Singapore).
	More information
	\textlink{https://ww5.aievolution.com/hbm1801/index.cfm?do=abs.viewAbs&abs=3300}{here}.

	\bigskip

	DuPre, E., Kundu, P., Esteban, O., Markello, R., Whitaker, K.,
	\textbf{Salo, T.}, \& Spreng, N. (2018).
	Introducing a BIDS-compliant multi-echo fMRI preprocessing pipeline.
	Presented at the 24\textsuperscript{th} annual meeting of the Organization
	for Human Brain Mapping (Singapore).
	More information
	\textlink{https://ww5.aievolution.com/hbm1801/index.cfm?do=abs.viewAbs&abs=2789}{here}.

	\bigskip

	Kohn, N., Riedel, M. C., \textbf{Salo, T.}, Laird, A. R., Eickhoff, S. B.,
	\& Morawetz, C. (2018).
	Meta-analytic brain networks underlying emotion regulation.
	Presented at the 24\textsuperscript{th} annual meeting of the Organization
	for Human Brain Mapping (Singapore).
	More information
	\textlink{https://ww5.aievolution.com/hbm1801/index.cfm?do=abs.viewAbs&abs=1262}{here}.

	\bigskip

	\textbf{Salo, T.}, Riedel, M. C., Bartley, J. E., Bottenhorn, K. L., Yarkoni, T.,
	Turner, M. D., Turner, J. A., Sutherland, M. T., \& Laird, A. R. (2017).
	A quantitative evaluation of Neurosynth's annotation methods. Presented at
	the 23\textsuperscript{rd} annual meeting of the Organization for Human Brain
	Mapping (Vancouver, British Columbia).
	More information
	\textlink{https://nbclab.github.io/posters/salo-neurosynth-poster}{here}.

	\bigskip

	Bartley, J. E., Riedel, M. C., \textbf{Salo, T.}, Boeving, E. R., Odean, R.,
	Bravo, E., Laird, R. W., Pruden, S., Brewe, E., Sutherland, M. E.,
	Laird, A. R. (2017).
	Understanding the neural substrates of physics problem solving: Brain
	mechanisms and behavior correlates. Presented at the 23\textsuperscript{rd}
	annual meeting of the Organization for Human Brain Mapping (Vancouver, British
	Columbia).
	More information
	\textlink{https://nbclab.github.io/posters/bartley-physics-poster}{here}.

	\bigskip

	Poudel, R.,  Riedel, M. C., Hill L. D, Flannery, J. F., \textbf{Salo, T.},
	Laird A.R., Sutherland M.T. (2017).
	Behavioral decoding of functionally related brain areas consistently linked
	to drug cue reactivity.
	Presented at Florida International University's 2017 Graduate Student
	Scholarly Forum (Miami, Florida).
	More information
	\textlink{https://nbclab.github.io/posters/poudel-cue-reactivity-poster}{here}.

	\bigskip

	Riedel, M. C., Poudel, R., \textbf{Salo, T.}, Eickhoff S. B., Fox, P. T.,
	Laird, A. R., \& Sutherland, M. T. (2016).
	Co-activation based parcellation of the human insula.
	Presented at the 22\textsuperscript{nd} annual meeting of the Organization
	for Human Brain Mapping (Geneva, Switzerland).
	More information
	\textlink{https://osf.io/pqvqy}{here}.

	\bigskip

	Lesh, T. A., Maddock, R. J., \textbf{Salo, T.}, Tanase, C., Ragland, J. D.,
	Niendam, T. A., Solomon, M., \& Carter, C. S. (2015).
	Diffusion Measures of Free Water and 1H-MRS Measures of Glutathione in First
	Episode Patients with Schizophrenia -- A Multi-Modal Investigation of an
	Inflammatory Model for Psychosis.
	Presented at the 15\textsuperscript{th} biennial meeting of the International
	Congress on Schizophrenia Research (Colorado Springs, CO) and at
	the annual meeting of the American College of Neuropsychopharmacology
	(Phoenix, AZ).

	\bigskip

	Phillips, R. C., \textbf{Salo, T.}, \& Carter, C. S. (2014).
	Default mode network activity precedes attention lapse in healthy subjects.
	Presented at the 44\textsuperscript{th} annual meeting of the Society for
	Neuroscience (Washington D.C.) and at the second annual Northern California
	Consciousness meeting (Davis, CA).

\end{hangparas}

\bigskip

\begin{center}\sectionstyle{HONORS AND AWARDS}\end{center}

\begin{minipage}[t]{.85\linewidth}
\flushleft
\noindent
Brain Initiative Principal Investigators Meeting Trainee Travel Award
\end{minipage}
\hfill
\begin{minipage}[t]{.15\linewidth}
\flushright
\noindent
\textsc{\textbf{2019}}
\end{minipage}

\begin{minipage}[t]{.85\linewidth}
\flushleft
\noindent
Organization for Human Brain Mapping Hackathon Travel Award
\end{minipage}
\hfill
\begin{minipage}[t]{.15\linewidth}
\flushright
\noindent
\textsc{\textbf{2017}}
\end{minipage}

\begin{minipage}[t]{.85\linewidth}
\flushleft
\noindent
Organization for Human Brain Mapping Merit Abstract Travel Award
\end{minipage}
\hfill
\begin{minipage}[t]{.15\linewidth}
\flushright
\noindent
\textsc{\textbf{2017}}
\end{minipage}

\bigskip

\begin{center}\sectionstyle{HACKATHONS}\end{center}

\begin{minipage}[t]{.85\linewidth}
\flushleft
\noindent
OHBM Hackathon
\end{minipage}
\hfill
\begin{minipage}[t]{.15\linewidth}
\flushright
\noindent
\textsc{\textbf{2019}}
\end{minipage}

\begin{minipage}[t]{.85\linewidth}
\flushleft
\noindent
Coastal Coding
\end{minipage}
\hfill
\begin{minipage}[t]{.15\linewidth}
\flushright
\noindent
\textsc{\textbf{2019}}
\end{minipage}

\begin{minipage}[t]{.85\linewidth}
\flushleft
\noindent
FIU Brainconn Hackathon
\end{minipage}
\hfill
\begin{minipage}[t]{.15\linewidth}
\flushright
\noindent
\textsc{\textbf{2018}}
\end{minipage}

\begin{minipage}[t]{.85\linewidth}
\flushleft
\noindent
BrainHack Montreal
\end{minipage}
\hfill
\begin{minipage}[t]{.15\linewidth}
\flushright
\noindent
\textsc{\textbf{2018}}
\end{minipage}

\begin{minipage}[t]{.85\linewidth}
\flushleft
\noindent
Code Rodeo
\end{minipage}
\hfill
\begin{minipage}[t]{.15\linewidth}
\flushright
\noindent
\textsc{\textbf{2018}}
\end{minipage}

\begin{minipage}[t]{.85\linewidth}
\flushleft
\noindent
OHBM Hackathon
\end{minipage}
\hfill
\begin{minipage}[t]{.15\linewidth}
\flushright
\noindent
\textsc{\textbf{2017}}
\end{minipage}

\begin{minipage}[t]{.85\linewidth}
\flushleft
\noindent
Neurohackweek
\end{minipage}
\hfill
\begin{minipage}[t]{.15\linewidth}
\flushright
\noindent
\textsc{\textbf{2016}}
\end{minipage}

\begin{bottompar}
	\begin{center}
		\headstyle{Last Compiled: \today}
	\end{center}
\end{bottompar}

\end{document}
